---
title: "DSSB Project on Heart Diseases"
subtitle: "Heart Disease Analysis and Predictions"
author: 
  Akshatha
  Doris
date: 2022-12-01
format: 
  html:
    code-fold: true
    standalone: true
    embed-resources: true
    toc: true
---

## Introduction

###### For this project we aim to analyse the heart disease dataset and predict whether a persons age and gender affect their risk of causing heart disease. The dataset we are using was downloaded from Kaggle websites that are set dates from 1988 till 2019 and consists of four databases: Cleveland, Hungary, Switzerland, and Long Beach V. It contains 76 attributes, including the predicted attribute, but all published experiments refer to using a subset of 14 of them. 

###### To achieve this, we make use of R Studio and required libraries to visualise, analyse and predict the dataset.

## Questions

#### 1) How do a person's age and gender affect their risk of heart disease? (Prediction)

#### 2) What are the other risk factors causing the heart disease?

#### 3) Are patients experiencing chest pain likely to have heart disease? 

#### 4) What kind of chest pain do heart patients experience? 


```{r}
#| label: packages-data
#| message: false  # We do not want to see the common tidyverse message in our document
# Load packages
library(dplyr)
library(tidyverse)
library(plotly)
library(ggplot2)
library(tidymodels)
library(modelsummary)
```

```{r}
df <- read_delim("data/heart.csv", show_col_types = FALSE)
df
view(df)
```

```{r}
summary(df)
```





